\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-05-15 doc/sw-system.tex
Described Spotters Guidee

Learning what lenses do: Spotter's Guide. Learning how
lenses work (science page, FAQ).

>>>>

The instant feedback provides real-time educational responses to the
volunteers as they start classifying; as well as this dynamic system, \sw
provides a static reference work for volunteers to consult when in doubt about
how to perform the task. This ``Spotter's Guide'' is a set of webpages showing
example lenses, both real and simulated, and also some common false positives,
drawn from the pool of survey images. The non-lenses were identified by three
of us (AV, AM and PM) while inspecting a small set of survey images in order
to define the ``dud'' training images. For easy reference, the lenses are
divided by type (for example, ``lensed galaxies,'' ``lensed quasars'' and
``cluster lenses''), as are the false positives (for example, ``Rings and
Spirals,'' ``Mergers,'' ``Artifacts'' and so on). The example images are
accompanied by explanatory text. The Spotter's Guide is reached via a button
on the left hand side, or the hyperlinked thumbnail images of the ``Quick
Reference'' provided on the right hand side, of the classification interface.

Most of the text of the Spotter's Guide focuses on what lenses do or don't do;
the website ``Science page'' contains a very brief introduction to how
gravitational lenses work, which is fleshed out a little on the ``FAQ'' page. 
This also contains answers to frequently asked questions about the interface
and the task set.
